Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-18 appendix.tex
sup

\oo{explain lower ERS with high eta? overfit.}

@@

\begin{comment}
FAT works on toy dataset only for adversarial DML.

Further experiments suggest very weak robustness and the
models are very prone to collapse due to the non-zero initial delta
(results in too hard adversarial example).

Gradient approximation does not work. Triplet gradient and ACT
gradient are convertible.

Does the new generic HM work under FAT?
	Previous FAT leads to collapse because (even if in the amdsemi +fat
	experiment due to implementation issue) the delta is going to be universal
	so that for every input $x$ it will increase $H[L(x)]$ as much as possible.
	This is too prone to lead to collpase. Can we reuse the gradient for 
	Hardness Manipulation then? We linearly scale down the delta?
	We want to minimize $E[|H_{src}(x)-H_{dst}(x)|]$ (to a specified hardness).
\end{comment}

@@

\oo{[TODO] arxiv 2105.04906 for collapse issue.}

>>>>

\noindent\ul{(1) Slight ERS decrease with a larger $\eta$}

In some cases, \eg, HM[$\mathcal{S},g_\mathsf{LGA}$]\&ICS on the CARS dataset
reaches a slightly lower ERS with $\eta=32$ compared to that with $\eta=8$.
%
We speculate this is because adversarial training suffers from overfitting~\cite{bagoftricks,overfitting}
on adversarial examples, as mentioned in Sec.~2.

@@

@@
